% Isaac Mayes's Resume
% Typeset using pdfLaTeX

\documentclass[9pt,letterpaper]{extarticle}

\RequirePackage{hyperref}

\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}

\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% Datestamp format (default): {yyyy}{MM}{dd} ---> MMM yyyy (e.g., Jan 2008).
\newcommand{\DatestampYMD}[3]{\mbox{\ShortMonth{#2} #1}}
\newcommand{\DatestampYM}[2]{\mbox{\ShortMonth{#2} #1}}
\newcommand{\DatestampY}[1]{#1}

% Abbreviations for months.
\newcommand{\ShortMonth}[1]{%
\ifcase#1\relax
\or Jan%
\or Feb%
\or Mar%
\or Apr%
\or May%
\or Jun%
\or Jul%
\or Aug%
\or Sep%
\or Oct%
\or Nov%
\or Dec%
\fi}

% PDF settings and properties.
\hypersetup{
pdftitle={Isaac Mayes's Resume},
pdfauthor={Isaac Mayes},
pdfcreator={pdfLaTeX},
pdfsubject={http://www.mayesid.com},
pdfproducer={},
pdfkeywords={Resume,CV,Isaac,Mayes,MayesIDevel,Software,Programmer,Developer,Engineer,C\#,CSharp,.NET,NET,dotnet,LaTeX},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

%
% Resume content starts here.
%
\begin{document}

\begin{center}
{\Huge \textbf{Isaac Mayes}}
\pdfbookmark[0]{Isaac Mayes}{PDF:IsaacMayes}

\href{https://www.google.com/maps/place/Austin,+TX+78728/}{Austin, TX, USA 78728}\ \textbullet
\ \href{http://www.mayesid.com}{www.mayesid.com}
\\
\href{tel:+15129537302}{+1\,(512)\,953-7302}\ \textbullet
\ \href{mailto:contact@mayesid.com}{contact@mayesid.com}
\pdfbookmark[1]{Contact Information}{PDF:ContactInformation}
\end{center}

\hrule
\vspace{-0.2em}
\subsection*{Technical Skills}
\pdfbookmark[1]{Technical Skills}{PDF:TechnicalSkills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Languages:]
	\pdfbookmark[2]{Languages}{PDF:Languages}
	C\#, SQL, PowerShell, Java, Python, \LaTeX
	\item[Technologies:]
	\pdfbookmark[2]{Technologies}{PDF:Technologies}
	.NET Framework, Entity Framework, SQL Management Objects (SMO), Active Directory Services (AD), Windows Communication Foundation (WCF), Internet Information Services (IIS), Windows Presentation Foundation (WPF), Windows Forms (WinForms), XML, NUnit, Moq, Apache log4net, Subversion (SVN)
	\item[Applications:]
	\pdfbookmark[2]{Applications}{PDF:Applications}
	Visual Studio, ReSharper, SQL Server Management Studio (SSMS), SQL Server Profiler, Visual Studio Code
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.2em}
\subsection*{Experience}
\pdfbookmark[1]{Experience}{PDF:Experience}

\begin{itemize}
	\parskip=0.1em

\item
	\pdfbookmark[2]{Signature Science}{PDF:SignatureScience}
	\headerrow
		{\textbf{\href{http://www.signaturescience.com/}{Signature Science}}}
		{\textbf{Austin, TX}}
	\pdfbookmark[3]{Database Developer/Full Stack Specialist}{PDF:DatabaseDeveloperFullStackSpecialist}
	\headerrow
		{\emph{Database Developer/Full Stack Specialist, \href{http://www.signaturescience.com/what-we-do/data-science-and-applied-statistics}{Data Science \& Quality Assurance Group}}}
		{\emph{\DatestampYM{2017}{06} -- Present}}
	\begin{itemize*}
		\item Design, develop, and maintain ASP.NET web applications.
		\item Design, develop, and maintain Oracle PL/SQL and MS SQL databases.
		\item Provide technical guidance and assistance to statisticians and scientists in regards to database access and operations.
	\end{itemize*}

	\item
	\pdfbookmark[2]{Computers Unlimited}{PDF:ComputersUnlimited}
	\headerrow
		{\textbf{\href{http://www.cu.net}{Computers Unlimited}}}
		{\textbf{Billings, MT}}
	\pdfbookmark[3]{Industrial Programmer}{PDF:IndustrialProgrammer}
	\headerrow
		{\emph{Programmer, \href{http://www.cu.net/industrial}{Industrial Group}}}
		{\emph{\DatestampYM{2014}{05} -- \DatestampYM{2017}{06}}}
	\begin{itemize*}
		\item Responsible for new and on-going development and support in several core applications, including: all security services and Active Directory integrations, user account set-up and authorization management applications, system set-up and system configuration applications, custom user-defined information management framework, SQL data migration framework, SQL data audit system, as well as an application for scheduling Batch processing jobs and the corresponding job execution service.
		\item Architecture Advocate for the Industrial Group since 2015. Attend weekly meetings with other architecture leads from each development group to discuss current development initiatives and programming standards. As well as serving as a point-of-contact for the Industrial group on architecture-related questions and discussion.
		\item Regularly work with Technical and Application Support teams on troubleshooting customer issues and improving applications.
		\item \textbf{Primary technologies:} C\#, .NET, SQL, Entity Framework, SMO, WCF, IIS, WPF, WinForms, AD, XML, PowerShell, Batch, log4net, NUnit, Moq, SVN, Visual Studio, ReSharper, SSMS, SQL Server Profiler, Windows Server 2008-12.
	\end{itemize*}
	\pdfbookmark[3]{Regression Intern}{PDF:RegressionIntern}	
	\headerrow
		{\emph{Intern, Regression/Automated QA Group}}
		{\emph{\DatestampYM{2014}{01} -- \DatestampYM{2014}{05}}}
	\begin{itemize*}
		\item Analyzed nightly unit test runs, assigned QA logs for broken tests, and compiled a daily report on the status of each build.
		\item Automated written test plans in a proprietary regression framework, and documented test plan details on an internal wiki.
		\item Assisted in the maintenance of internal tools used by Regression, including improvements to the Regression Testing Framework.
		\item \textbf{Primary technologies:} C\#, .NET, SQL, WinForms, XML, NUnit, Moq, SVN, Visual Studio, SSMS, Windows Server 2008-12.
	\end{itemize*}

	\item
	\pdfbookmark[2]{Rocky Mountain College}{PDF:Experience-RockyMountainCollege}
	\headerrow
		{\textbf{\href{http://www.rocky.edu}{Rocky Mountain College}}}
		{\textbf{Billings, MT}}
	\pdfbookmark[3]{Website Administrator  (The Summit)}{PDF:WebsiteAdmininistrator_Summit}
	\headerrow
		{\emph{Website Administrator, \href{http://summit.rocky.edu}{Student Publications}}}
		{\emph{\DatestampYM{2013}{01} -- \DatestampYM{2013}{05} \& \DatestampYM{2014}{01} -- \DatestampYM{2014}{05}}}
	\begin{itemize*}
		\item Administrated the website for the student newspaper, The Summit, during all active periods from 2013 through spring 2014.
		\item Worked with editors to post news content, pictures, and articles on a regular basis; coinciding with publications of the paper.
		\item Maintained the website's WordPress install, and managed changes to improve the users' experience and website functionality.
	\end{itemize*}
%	\pdfbookmark[3]{Paid Note-Taker}{PDF:PaidNoteTaker}
%	\headerrow
%		{\emph{Paid Note-Taker, \href{https://www.rocky.edu/student-life/student-support/academic-support/ServicesAcademicSuccess.php}{Services for Academic Success}}}
%		{\emph{\DatestampYM{2013}{09} -- \DatestampYM{2013}{12}}}
%	\begin{itemize*}
%		\item Required to take complete, detailed, well-written notes for use by students requiring additional academic assistance.
%		\item Responsible for submitting photocopies of all notes taken on a weekly deadline.
%		\item Notes taken for the \href{https://www.rocky.edu/academics/catalog/program/9/Computer_Science#courses-content}{Computer Science classes: CSC 351 (Algorithms), and CSC 352 (Programming Language Study I - Python)}.
%	\end{itemize*}
	\pdfbookmark[3]{By-Appointment Tutor}{PDF:ByAppointmentTutor}
	\headerrow
		{\emph{By-Appointment Tutor, \href{https://www.rocky.edu/student-life/student-support/academic-support/ServicesAcademicSuccess.php}{Services for Academic Success}}}
		{\emph{\DatestampYM{2012}{09} -- \DatestampYM{2014}{05}}}
	\begin{itemize*}
		\item Held appointments with students, on request, to best fit their schedules and tailor aid according to their individual needs.
		\item Promoted the understanding of core concepts and best practices, and assisted with technical questions on syntax and semantics in programming assignments.
		\item Services primarily requested by students taking \href{https://www.rocky.edu/academics/catalog/program/9/Computer_Science#courses-content}{freshman-level introductory courses (CSC 130/131)}.
	\end{itemize*}
	\pdfbookmark[3]{System Administrator}{PDF:SystemAdministrator_CSDept}
	\headerrow
		{\emph{System Administrator, \href{http://cs.rocky.edu}{Computer Science Department}}}
		{\emph{\DatestampYM{2012}{03} -- \DatestampYM{2014}{05}}}
	\begin{itemize*}
		\item Handled network troubleshooting, assisted users with account and software issues, and researched improvements to be made.
		\item Physically maintained the computer lab set-up by routing cables, installing UPSs, and replacing old or faulty hardware.
		\item Updated and installed new software, including a major OS version upgrade to OS X Mavericks, on all machines.
	\end{itemize*}
	\pdfbookmark[3]{Help Desk Assistant}{PDF:HelpDeskAssistant}
	\headerrow
		{\emph{Help Desk Assistant, \href{https://rocky.edu/student-life/student-support/academic-computing/}{Academic Computing}}}
		{\emph{\DatestampYM{2011}{09} -- \DatestampYM{2013}{05}}}
	\begin{itemize*}
		\item Maintained campus printers and computer lab PCs; including the restoration and configuration of damaged and new machines.
		\item Aided students with troubleshooting networking issues in on-campus housing: from configuring routers, to handling port issues on the buildings' network switches.
		\item Provided technical support for staff and students in a timely manner through an online support ticket system, and in-person.
	\end{itemize*}
%	\pdfbookmark[3]{Website Administrator (CS Department)}{PDF:WebsiteAdministrator_CSDepartment}
%	\headerrow
%		{\emph{Website Administrator, \href{http://cs.rocky.edu/programming-competitions/high-school-competions/}{Computer Science Department}}}
%		{\emph{\DatestampYM{2010}{09} -- \DatestampYM{2011}{05}}}
%	\begin{itemize*}
%		\item Restructured the Computer Science department's website for their annual High School Programming Competitions.
%		\item Archived and organized media content, including: pictures, videos, problem sets, and results from past competitions.
%		\item Updated the website's WordPress installation, plugins, and theme, in order to improve the accessibility of the content.
%	\end{itemize*}
\end{itemize}


\hrule
\vspace{-0.2em}
\subsection*{Education}
\pdfbookmark[1]{Education}{PDF:Education}

\begin{itemize}
	\parskip=0.1em

	\item
	\pdfbookmark[2]{Rocky Mountain College}{PDF:Edu_RockyMountainCollege}
	\headerrow
		{\textbf{\href{http://www.rocky.edu/}{Rocky Mountain College}}}
		{\textbf{Billings, MT}}
	\pdfbookmark[3]{Bachelor of Science in Computer Science}{PDF:BSinCS}
	\headerrow
		{\emph{Bachelor of Science in \href{http://cs.rocky.edu/}{Computer Science}}}
		{\emph{\DatestampYM{2010}{08} -- \DatestampYM{2014}{05}}}
	\textbf{Primary technologies:} Java 6/7, Swing, Concurrent Versions System (CVS), NetBeans, Mac OS X
\end{itemize}

\end{document}
